Periodograms for Multiband Astronomical Time Series

### 2015-01-30 writeup/paper.tex
fixed two typos in sec 7.1

In the PGLS model, they start with a multi-phase model, fitting independent $N=1$ term fits to each band, and apply a nonlinear regularization term which penalizes differences in the amplitude and phase. In terms of the formalism used in this work, the PGLS model minimizes a regularized $\chi^2$ of the form
\begin{equation}
  \chi^2_{PGLS} = \sum_{k=1}^K \bigg[~\chi^2_{GLS}(D^{(K)}) + J_A(A^{(k)}) + J_\phi(\phi^{(k)})~\bigg].
\end{equation}
for $K$ bands, where $\chi^2_{GLS}(D^{(K)})$ is the $\chi^2$ of the standard floating mean model on the single-band data $D^{(K)}$, and $J_A$ and $J_\phi$ are regularization/penalty terms which are a function of the amplitude $A^{k}$ and phase $\phi^{(k)}$ of each model. In terms of our linear model parameters $\theta^{(k)}$, this amplitude and phase can be expressed:
\begin{eqnarray}
 A^{(k)} &=& \sqrt{(\theta_1^{(k)})^2 + (\theta_1^{(k)})^2}\nonumber\\
 \phi^{(k)} &=& \arctan(\theta_2 / \theta_1)
\end{eqnarray}
The selected form of these regularization terms penalizes deviations of the amplitude and phase from a common mean between the bands; in this sense the PGLS model can be considered a conceptual mid-point between our shared-phase and multi-phase models. Within the formalism proposed here, such a mid-point may be alternatively attained by suitably increasing the regularization parameter $\epsilon$ used in the shared-phase model, though the nature of the resulting regularization will differ.

>>>>

In the PGLS model, they start with a multi-phase model, fitting independent $N=1$ term fits to each band, and apply a nonlinear regularization term which penalizes differences in the amplitude and phase. In terms of the formalism used in this work, the PGLS model minimizes a regularized $\chi^2$ of the form
\begin{equation}
  \chi^2_{PGLS} = \sum_{k=1}^K \bigg[~\chi^2_{GLS}(D^{(K)}) + J_A(A^{(k)}) + J_\phi(\phi^{(k)})~\bigg].
\end{equation}
for $K$ bands, where $\chi^2_{GLS}(D^{(K)})$ is the $\chi^2$ of the standard floating mean model on the single-band data $D^{(K)}$, and $J_A$ and $J_\phi$ are regularization/penalty terms which are a function of the amplitude $A^{k}$ and phase $\phi^{(k)}$ of each model. In terms of our linear model parameters $\theta^{(k)}$, this amplitude and phase can be expressed:
\begin{eqnarray}
 A^{(k)} &=& \sqrt{(\theta_1^{(k)})^2 + (\theta_1^{(k)})^2}\nonumber\\
 \phi^{(k)} &=& \arctan(\theta_2 / \theta_1)
\end{eqnarray}
The selected form of these regularization terms penalizes deviations of the amplitude and phase from a common mean between the bands; in this sense the PGLS model can be considered a conceptual mid-point between our shared-phase and multi-phase models. Within the formalism proposed here, such a mid-point may be alternatively attained by suitably increasing the regularization parameter $\epsilon$ used in our shared-phase model, though the nature of the resulting regularization will differ.
